### 2024-08-29 docs/manuscript.tex
Adding line numbers.

\usepackage{float}
\usepackage{graphicx}
\usepackage{caption}
\usepackage[hyphens]{url}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{amsmath}
\graphicspath{{figures/}}
\setlength{\abovecaptionskip}{15pt plus 3pt minus 2pt}

@@

\Keywords{} % Keywords - if you don't want any simply remove all the text between the curly brackets
\newcommand{\keywordname}{Keywords} % Defines the keywords heading name

@@

@@

>>>>

\usepackage{float}
\usepackage{graphicx}
\usepackage{caption}
\usepackage[hyphens]{url}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage[switch,pagewise]{lineno}
\linenumbers

\graphicspath{{figures/}}
\setlength{\abovecaptionskip}{15pt plus 3pt minus 2pt}

@@

\Keywords{
Bioinformatics,
Software Tool Development, 
Interdisciplinary Research, 
Departmental Affiliation, 
Software Accuracy, 
Medical Informatics, 
Academic Expertise, 
Benchmarking,
Computational Biology
} % Keywords - if you don't want any simply remove all the text between the curly brackets
\newcommand{\keywordname}{Keywords} % Defines the keywords heading name

@@

\section*{Key Points}

\begin{itemize}
\item The study investigates the relationship between academic department affiliations of authors and the accuracy of bioinformatic software tools they develop.
\item Results indicate no statistically significant association between departmental affiliation and the accuracy of bioinformatic tools, challenging the assumption that departmental expertise predicts software quality.
\item Tools from the "Medical Informatics" field showed a higher mean proportion of wins, while those from "Bioinformatics" and "Engineering" fields ranked lower, though these differences were not statistically significant after correcting for multiple-testing.
\item The findings suggest that allocating sufficient resources for long term software development are more critical to accurate bioinformatic tools than departmental expertise.
\end{itemize}

@@

%Generate a doi:
%https://docs.github.com/en/repositories/archiving-a-github-repository/referencing-and-citing-content
%https://zenodo.org/account/settings/github/
